Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-11-23 paper/main.tex
shorten review of anterior vs. posterior PPA

% brain mapping via fMRI
Humans can perceive and make sense of their daily environment casually and
seemingly without any effort. Cognitive neuroscientists use brain imaging
techniques to map perceptual and cognitive processes (e.g. seeing and
recognizing faces; \citep{kanwisher1997ffa}) to functional brain areas or
networks.
% What is the PPA?
A classic example of a higher-level visual area is the ``parahippocampal place
area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}, and thus not anatomically but functionally
defined:
% neural correlate of scene perception
increased hemodynamic activity is observed in the PPA when subjects view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
tools or faces) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
epstein1998ppa}.

@@

% intro
Results of the AO contrasts consistently yielded significant clusters spatially
constrained to the anterior part of both the PPA group overlap and significant
clusters of the AV contrasts.

% but
Previous studies suggest that the PPA is not a functionally homogeneous area but
consists of submodules that ``activate selectively to scenes'' and ``cooperate
to build a complete representation of a scene''
\citep{baldassano2013differential}.

%
The anterior and posterior PPA show:
% connectivity
a) differences in connectivity profiles [Nasr et al., 2013; Silson et al.,
2016a] \citep{baldassano2013differential, baldassano2016two},
% low-level scene features
b) different responses to low-level scene features [Nasr et al., 2014; Silson et
al., 2015; Baldassano et al., 2016a,b; Watson et al.,
2016]\citep{baldassano2016two},
% high-level scene features
c) different responses to high-level scene features [Park et al., 2014; Aminoff
and Tarr, 2015; Linsley and Macevoy, 2015; Marchette et al.,
2015]\citep{baldassano2016two},
% scenes vs abstract objects
c) a gradient in functional sensitivity to scenes and abstract object stimuli
\citep{arcaro2009retinotopic, aminoff2007parahippocampal,
baldassano2013differential}, and
% TMS
e) differences in stimulation studies [+++Rafique et al.,
2015+++]\citep{baldassano2016two}.  \paragraph{posterior PPA}

% connectivity
The posterior PPA is more strongly functionally connected to the occipital
visual cortex, including lateral occipital cortex (LOC) and transverse occipital
sulcus (TOS) \citep{baldassano2013differential, baldassano2016two}.
% LOC and TOS
These regions have well-defined retinotopic maps [+++Arcaro et al., 2009; Nasr
et al., 2011+++], and are associated with the perception of low-level visual
features and object shape \citep{baldassano2013differential}.

% object sensitivity
lower-level features: The pPPA is more responsive to both simple visual textures
and (abstract) objects \citep{arcaro2009retinotopic,
baldassano2013differential}:
%
The pPPA responded about four times as strongly to a flickering checker-board
stimulus compared to an anterior portion \citep{arcaro2009retinotopic}.
%
The response to objects was greater than the response to scrambled images only
in the posterior portion \citep{arcaro2009retinotopic}.

%
high-level features: Higher-level visual features also drive response patterns
in these regions [Bryan et al., 2016].

\paragraph{anterior PPA}

The anterior PPA is more strongly functionally connected to the RSC and parietal
cortices (caudal inferior parietal lobe; cIPL; cIPL was defined using the
Eickhoff–Zilles PGp probabilistic cytoarchitectonic map)[, medial PFC, and the
lateral surface of the anterior temporal lobe]
\citep{baldassano2013differential, baldassano2016two}.

\citep{baldassano2016two} The aPPA is
% category
a) driven more by high-level category information than by spatial frequency
content [Watson et al., 2016],
% locations
b) to represent real-world locations (even from perceptually distinct views)[
Marchette et al., 2015],
% associations
c) to encode object co-occurrences [Aminoff and Tarr, 2015], and
% scene size
d) to represent real-world physical scene size [Park et al., 2014]
\citep{baldassano2016two}.

% object sensitivity
The aPPA is less visually responsive to both scenes and objects, with notably
low sensitivity to abstract object stimuli \citep{baldassano2013differential}.
%
Results suggest that aPPA may be more concerned with global scene properties
(such as spatial expanse) and non-object-based scene properties than posterior
PPA \citep{baldassano2013differential}.

% spaciousness
Its representation of scene spaciousness draws on prior knowledge about the
typical size of different scene categories, since it is affected by the presence
of diagnostic objects [Linsley and Macevoy, 2015]\citep{baldassano2016two}.

@@

%
although our data suggest that PPA might contain identifiable subregions, these
subregions should not be considered as completely independent modules. Both
subregions activate selectively to scenes, and the parahippocampal region (at
least in macaques) is densely self-connected (Suzuki 2009), implying that these
subregions cooperate to build a complete representation of a scene.
%
Their distinct connectivity properties, however, do suggest that each may be
involved in specific aspects of visual and cognitive processing involved in the
overarching goal of scene understanding.

%
The fact that anterior PPA had a lower sensitivity to our abstract object
stimuli does not necessarily imply that this region does not use object
information\citep{baldassano2013differential}.
%
Previous work has shown that PPA responds to objects that have spatial
associations [Aminoff et al. 2007], are space-defining [Mullally and Maguire
2011], and are navigationally-relevant [Janzen and Van Turennout 2004].
%
These types of responses require spatial memory and cannot be based purely on
visual features like object shape. If anterior PPA is involved in processing
spatial context, then space-defining or navigationally-relevant objects could
activate anterior PPA more strongly than our abstract objects, which were
unfamiliar and provided no sense of context or orientation.
%
Further experiments will be required to determine whether what type of
object-related information is used in this region
\citep{baldassano2013differential}.

@@

We suggest that the aPHC encodes incoming information in an amodal format and
acts as an interface with other memory regions, including the hippocampal,
retrosplenial, and perirhinal memory systems (see Ranganath and Ritchey, 2012,
for an review)\citep{baumann2016functional}.

\subsubsection{RSC (in both stimuli)}

@@

% but RSC
Apart from the PPA, we find significantly increased activity consistently across
contrast of both contrasts in the retrosplenial cortex (RSC).

% location functionally defined
In context of a scene-responsive region, the RSC is functionally defined and not
necessarily identical to the anatomically defined retrosplenial cortex [26]
\citep{epstein2008parahippocampal}.
% location
The RSC is located in the retrosplenial cortex, and posterior cingulate region,
near to the point where the calcarine sulcus joins the parietal-occipital sulcus
\citep{epstein2008parahippocampal}.
% anatomy of real RSC
The Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by
the posterior cingulate (BA 23 and 31) [51–56]
\citep{epstein2008parahippocampal}.
% function
RSC is strongly active during scene viewing, scene imagery [25] and mental
imagination of navigation through familiar environments [8]
\citep{epstein2008parahippocampal}.

% Aminoff 2013
Processing of strong, long-term, contextual associations elicits activity within
the PHC, as well as the RSC (which includes regions of the retrosplenial cortex,
extending into the posterior cingulate cortex, and the precuneus), the medial
prefrontal cortex (MPFC), and the transverse occipital sulcus (TOS) (Figure 2)
[2,3,59–67] \citep{aminoff2013role}.

% discussion of what the RSC does
\todo[inline]{interpretation: cf.\citep{vann2009what} and paper that reference
her}
% conclusion
\todo[inline]{conclusion?}

@@

%
\citep{baldassano2016two} functional difference pPPA vs. OPA: functional
distinction between pPPA and OPA is currently unclear. Previous work has
speculated about the purpose of the apparent ventral and dorsal ``duplication''
of regions sensitive to large landmarks, proposing that it may be related to
different output goals (e.g., action planning in OPA, object recognition in
pPPA)[Konkle and Caramazza, 2013], or to different input connections (e.g.,
lower visual field processing in OPA, upper visual field processing in
pPPA)[Kravitz et al., 2013; Silson et al., 2015]. OPA and pPPA may also use
information from different visual eccentricities: OPA processing less
peripheral, relatively high-resolution environmental features. pPPA processing
more peripheral, large-scale geometry, and context [Baldassano et al.,
2016a]\citep{baldassano2016two}.

>>>>

% brain mapping via fMRI
Humans can perceive and make sense of their daily environment casually and
seemingly without any effort. Cognitive neuroscientists use brain imaging
techniques to map perceptual and cognitive processes (e.g. seeing and
recognizing faces; \citep{kanwisher1997ffa}) to functional brain areas or
networks.
% What is the PPA?
A classic example of a higher-level visual area is the ``parahippocampal place
area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}, and thus not anatomically but functionally
defined:
% neural correlate of scene perception
increased hemodynamic activity is observed in the PPA when subjects view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
tools or faces) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
epstein1998ppa, troiani2012object}.

@@

% intro
Results of the AO contrasts consistently yielded significant clusters spatially
constrained to the anterior part of the PPA group overlap (and to the anterior
part of significant clusters of the AV contrasts).
% PPA might have submodules
Previous studies provide evidence that the posterior PPA (pPPA) and anterior PPA
(aPPA) show differences in both functional connectivity profiles and in
response to low- and high-level visual features.

% posterior connectivity
The pPPA is more strongly functionally connected to the occipital visual cortex
\citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% functionality
The pPPA is functionally more responsive than aPPA to low-level features of
(abstract) objects or scenes \citep{baldassano2013differential,
nasr2014thinking, rajimehr2011parahippocampal}.

% anterior
The anterior PPA is more strongly functionally connected to portions of the
default mode network, including caudal inferior parietal lobe (cIPL), the
restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
temporal lobe \citep{baldassano2013differential, baldassano2016two}
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
The aPPA is functionally more responsive than pPPA to high-level features of
objects (e.g. spatial contextual associations
\citep{aminoff2007parahippocampal, aminoff2015associative} and scenes (e.g.
real-word size \citep{park2015parametric}; a scene's abstract identity/category
\citep{marchette2015outside, watson2016patterns}).

@@

data suggest that the PPA is not a ally homogeneous area buconsists of
submodules that ``activate selectively to scenes'' and ``cooperate to build a
complete representation of a scene'' \citep{baldassano2013differential}.

%
Our data suggest that PPA might contain identifiable subregions, but these
subregions should not be considered as completely independent modules.
%
Both subregions activate selectively to scenes, and the parahippocampal region
(at least in macaques) is densely self-connected (Suzuki 2009), implying that
these subregions cooperate to build a complete representation of a scene.
%
Their distinct connectivity properties, however, do suggest that each may be
involved in specific aspects of visual and cognitive processing involved in the
overarching goal of scene understanding.

%
The fact that anterior PPA had a lower sensitivity to our abstract object
stimuli does not necessarily imply that this region does not use object
information \citep{baldassano2013differential}.
%
Previous work has shown that PPA responds to objects that have spatial
associations [Aminoff et al. 2007], are space-defining [Mullally and Maguire
2011], and are navigationally-relevant [Janzen and Van Turennout 2004].
%
These types of responses require spatial memory and cannot be based purely on
visual features like object shape. If anterior PPA is involved in processing
spatial context, then space-defining or navigationally-relevant objects could
activate anterior PPA more strongly than our abstract objects, which were
unfamiliar and provided no sense of context or orientation.
%
Further experiments will be required to determine whether what type of
object-related information is used in this region
\citep{baldassano2013differential}.

@@

We suggest that the aPHC encodes incoming information in an amodal format and
acts as an interface with other memory regions, including the hippocampal,
retrosplenial, and perirhinal memory systems (see Ranganath and Ritchey, 2012,

\subsubsection{retrosplenial cortex (RSC)}

@@

% but RSC
Apart from the PPA, we find significantly increased activity consistently across
contrast of both contrasts in the retrosplenial cortex (RSC).
% location functionally defined
As a scene-responsive region, the RSC is functionally defined and not
necessarily identical to the anatomically defined retrosplenial cortex [26]
\citep{epstein2008parahippocampal}.
% function
The RSC is strongly active during scene viewing, scene imagery [25] and mental
imagination of navigation through familiar environments [8]
\citep{epstein2008parahippocampal}.
% location
The RSC is located in the retrosplenial cortex, and posterior cingulate region,
near to the point where the calcarine sulcus joins the parietal-occipital sulcus
\citep{epstein2008parahippocampal}.
% anatomy of real RSC
The Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by
the posterior cingulate (BA 23 and 31) [51–56]
\citep{epstein2008parahippocampal}.

% discussion of what the RSC does
interpretation cf.: \citep{vann2009what, chrastil2018heterogeneity,
silson2019posterior}
% conclusion

@@

%
\citep{baldassano2016two} regarding functional difference pPPA vs. OPA:
functional distinction between pPPA and OPA is currently unclear. Previous work
has speculated about the purpose of the apparent ventral and dorsal
``duplication'' of regions sensitive to large landmarks, proposing that it may
be related to different output goals (e.g., action planning in OPA, object
recognition in pPPA)[Konkle and Caramazza, 2013], or to different input
connections (e.g., lower visual field processing in OPA, upper visual field
processing in pPPA)[Kravitz et al., 2013; Silson et al., 2015]. OPA and pPPA may
also use information from different visual eccentricities: OPA processing less
peripheral, relatively high-resolution environmental features. pPPA processing
more peripheral, large-scale geometry, and context [Baldassano et al.,
2016a] \citep{baldassano2016two}.
